\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Brandon Blaylock}

\section{Work experience}

\begin{eventlist}

\item{October 2006 -- Present}
     {Keyboard Cowboys}
     {IT Consultant}

Operating and managing a consulting firm focused on \textbf{systems
administration}, \textbf{web design}, \textbf{hosting}, hardware
and software \textbf{break fix}, \textbf{full stack development},
\textbf{network administration}, \textbf{system workflow design},
and \textbf{performance analysis} for small and medium
sized businesses. Clients range in size from individual home
users to businesses with 20+ servers and 100+ desktops under
service.

\item{September 2013 -- December 2015}
     {Shoutpoint}
     {Systems Administrator}

Built out and \textbf{maintained critical infrastructure} components
including \textbf{servers}, \textbf{networking equipment}, host operating
systems, \textbf{virtual machines}, \textbf{application configurations},
and \textbf{application deployment}. \textbf{Developed internal tools}
in \textbf{Bash} and \textbf{Node.js} for the automation of the virtual
machine build system. This tool required coordinating resources
across 5 geographically diverse data centers. Developed and
implemented tools that managed and updated internal \textbf{yum and
apt repositories} as well as handled the regular deployment of
\textbf{Puppet} infrastructure and application code.

\item{August 2007 -- August 2010}
     {GoDaddy.com}
     {Data Center Technician}

Was responsible for the build out and maintenance of \textbf{enterprise
level data centers} across a private MAN. \textbf{Trained} and assessed
the skills of junior technicians in proprietary software, hardware
proficiency, and company workflow. \textbf{Headed critical deployments}
for front of site and infrastructure upgrades for the datacenter team.
Acted as \textbf{final tier of customer support} for dedicated and
virtual machine customers. Compiled and edited all internal documentation
created by the datacenter team. Created and maintained the data center
team \textbf{knowledge base}.

\item{August 2001 -- August 2004}
     {Magenta Computer}
     {Technician}

Was responsible for \textbf{parts inventory}, custom desktop and
\textbf{server manufacturing}, hardware and software
\textbf{troubleshooting}, and \textbf{data recovery}.

\end{eventlist}


\personal
    [null.pub]
    {Mission Viejo, CA}
    {+1 (949) 288-3884}
    {brandon@null.pub}

\section{Education}

\begin{yearlist}

\item[B.S. Mathematics]{2014 -- 2017}
     {Undergraduate Studies}
     {University of California, Irvine}

\end{yearlist}

\section{Projects}

\begin{yearlist}

\item{2015}
     {nullbot (\href{https://github.com/baetheus/nullbot}{github.com})}
     {Telegram Bot}

\item{2015}
     {shoutapi (\href{https://github.com/baetheus/shoutapi}{github.com})}
     {Shoutpoint API Library}

\item{Ongoing}
     {beer (\href{https://beer.null.pub}{beer.null.pub})}
     {Beer Experiments}

\end{yearlist}

\section{Languages}

\begin{factlist}
\item{English}{Native speaker}
\item{French}{Oral: fair -- Written: good}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Excellent}
     {Node.js, Python, Linux, Illumos(Solaris), Unix, Windows, DNS,
     Puppet, TFTP, DHCP, Nginx, Xen, Ipfilter, Ansible, ZFS, dtrace,
     Bash, OSX}

\item{Intermediate}
     {Python, FreeBSD, MySQL, Redis, Apache, \LaTeX, \TeX}

\item{Basic}
     {Photoshop, SolidWorks}

\end{factlist}

\section{Hardware Skills}

\begin{factlist}

\item{Excellent}
     {Dell x86 Servers, Serial Connection Pinouts, Apple Hardware,
     Data Center Design, Fiber and Copper cabling, Teensy 2.0,
     Beaglebone Black}

\item{Intermediate}
     {CHIP, Teensy 3.2}

\end{factlist}

\end{document}
