\documentclass{article}
\usepackage[a4paper, left=0.5in, right=0.5in, top=1in, bottom=1in]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage{multicol, fancyhdr, hyperref, parskip}

\parskip=1em

%%% \split{Top Left}{Bottom Left}{Bottom Right}
\newcommand{\split}[3]{
\noindent\begin{tabular}[t]{@{}l}
    \textbf{#1} \\ #2
\end{tabular}
\hfill
\begin{tabular}[t]{l@{}}
    \\
    \textit{#3}
\end{tabular}
\noindent\rule{\columnwidth}{0.5pt}
}

%%% \sub{Title}
\newcommand{\sub}[1]{
    {\raggedleft
        \large{\textsc{\color{OliveGreen}#1}}\par
    }
}

%%% Header
\pagestyle{fancy}
\fancyhf{}
\lhead{\Huge{\textbf{Brandon Blaylock}}}
\rhead{\color{OliveGreen}\small{(949) 288-3884 $\cdot$ \href{mailto:brandon@blaylock.dev}{brandon@blaylock.dev} $\cdot$ \href{https://blaylock.dev}{https://blaylock.dev} }}
\rfoot{Last updated \today.}

\begin{document}
\begin{multicols}{2}

\sub{Work Experience}

\split{Quick Quack Car Wash}{Software Engineer}{May 2020 - August 2021}
\textbf{Interviewed, onboarded, and trained} multiple engineers.
\textbf{Planned} and \textbf{led} several greenfield projects and rewrites into
production, including automating physical gates and sales using license plate
recognition. Introduced \textbf{living documentation} and \textbf{automated
testing} to all products.

\split{Ntersol}{Senior Frontend Engineer}{July 2019 - December 2019}
Implemented \textbf{functional programming} paradigms in \textbf{Angular}.
Defined and implemented standard practices for \textbf{api integration},
\textbf{ui structure}, and \textbf{semantic component design}. Created code
generators for \textbf{api validation}, \textbf{error handling},
\textbf{logging}, and \textbf{caching} in frontend applications.

\split{Lodasoft}{Senior Software Engineer}{July 2018 - July 2019} Designed and
built highly dynamic \textbf{white labelled} web portals for loan agents and
borrowers to manage document submission and validation.  Implemented
\textbf{batched logging} from the front end, a front end \textbf{monorepo},
and \textbf{application documentation} practices.

\split{Loan Depot}{Senior Software Engineer}{January 2018 -- July 2018} Built
the highest traffic customer portal application in \textbf{Angular} along with
two other production applications. Documented and implemented \textbf{best
practices} for front end engineering to enable better \textbf{code sharing},
\textbf{small compilation} bundles, and \textbf{robust coding standards}.

\split{Voxology}{Software Engineer}{May 2017 -- Dec 2017} Frontend and
middleware software engineer. Built applications using \textbf{AngularJS},
\textbf{Angular}, \textbf{Typescript}, \textbf{Ngrx}, \textbf{Nodejs},
\textbf{Express}, \textbf{rxjs}, and a large collection of open source
libraries. I also collaborated with the IT team towards implementing
\textbf{containerization} and starting a migration to \textbf{Kubernetes}. I
established Angular standard practices including \textbf{reactive forms
design}, \textbf{component encapsulation}, \textbf{templatization}, and
\textbf{project architecture}.

\split{Shoutpoint}{Systems Administrator}{Sept 2013 -- Dec 2015} Designed and
maintained infrastructure. Developed internal IT tooling (\textbf{Bash},
\textbf{Node.js}, \textbf{Xen} automation). Used \textbf{Ansible},
\textbf{Ansible Playbooks}, and \textbf{Custom Ansible Modules} to deploy vms
and internal applications. Built tooling to manage \textbf{yum} and
\textbf{apt} repositories and deployment of Puppet manifests. Worked heavily
with \textbf{Puppet}, specifically to manage \textbf{DNS} and \textbf{NTP}
servers.

\iffalse
% The following jobs no long fit on the single page resume

\split{Keyboard Cowboys}{Consultant / Software Engineer}{Oct 2006 - Present}
Offered consulting services covering \textbf{software engineering},
\textbf{systems administration}, \textbf{custom application development},
\textbf{break fix}, and general \textbf{web development}.

\split{GoDaddy.com}{Data Center Engineer}{Aug 2007 -- Aug 2010} Was
responsible for the build out and maintenance of \textbf{enterprise level data
centers}. \textbf{Trained} junior technicians. \textbf{Headed critical
deployments} for the data center team. Acted as the \textbf{final tier of
customer support}. Created and maintained the data center team
\textbf{knowledge base}.

\split{Magenta Computer}{Technician}{Aug 2001 -- Aug 2004} \textbf{Server
manufacturing}, hardware and software \textbf{troubleshooting}, and
\textbf{data recovery}. I cut my teeth here on everything from Intel's 486DX2
to the first Xeons and beyond.  \fi

\columnbreak

\sub{Summary} I am a software engineer with experience troubleshooting bare
metal, tracking down network and protocol gremlins, writing full featured css
libraries, and most things between. I'm language and tech stack agnostic with
the exception that I dislike bloat, opaque systems, and esoteric processes. My
favorite things in a job are complex problems, understandable solutions, and
good people.

\sub{Software Skills} \begin{tabular}{r|p{61mm}} \textsc{Excellent} &
Javascript, TypeScript, Go, Bash, Deno, Node.js, Angular, Ngrx, React,
Redux, SmartOS, macOS, Linux, Windows \\ \textsc{Intermediate} & Nix, Docker,
Kubernetes, Python, Rust, MySQL, dtrace, Redis, Apache, \LaTeX, \TeX \\
\textsc{Basic} & Photoshop, SolidWorks \end{tabular}

\sub{Hardware Skills} \begin{tabular}{r|p{61mm}} \textsc{Excellent} & x86,
Serial Connection Pinouts, Apple Hardware, Data Center Design, Fiber and Copper
cabling, Teensy 2.0, Beaglebone Black \\ \textsc{Intermediate} & CHIP, Teensy
3.2 \end{tabular}

\sub{Public Projects}
\split{@nll/fun}{\href{https://github.com/nullpub/fun}{github.com/nullpub/fun}}{Ongoing}
A utility library for writing functional style code in TypeScript for the Deno
runtime. Wide ranging and well tested.

\split{@nll/datum}{\href{https://github.com/nullpub/datum}{github.com/nullpub/datum}}{Recent}
An abstract data type in the style of fp-ts. It represents the Option (or
Maybe) type with the added cross product of a pending state.

\split{Bee}{\href{https://github.com/baetheus/bee}{github.com/baetheus/bee}}{Recent}
A long lived clone of the New York Times Spelling Bee game.

\sub{Education} \split{Bachelors of Science in Mathematics}{University of
California, Irvine}{2014 - 2017} \textit{Incomplete} My focus is in pure
math with particular attention paid to Abstract Algebra and Galois Theory.

\end{multicols}

\end{document}
